%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Rohit Varkey Thankachan}{
\href{mailto:rohitvarkey@gatech.edu}{rohitvarkey@gatech.edu} | 404.579.3137\\
\urlstyle{same}\url{https://rohitvarkey.github.io} | \href{https://github.com/rohitvarkey}{github.com/rohitvarkey} \\ 
\url{https://linkedin.com/in/rohitvarkey}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.48\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\runsubsection{Georgia Institute of Technology\\}
\descript{Masters in Computer Science}
\location{Expected May 2018 | Atlanta, GA}
\sectionsep

\runsubsection{National Institute of Technology Karnataka\\}
\descript{Bachelors in Computer Engineering}
\location{May 2016 | GPA: 8.4/10.0 | Surathkal, India }

\section{Experience}

\runsubsection{Julia Summer of Code}
\descript{| Open Source Contributor }
\location{June 2015 – Aug 2015 | Remote, Kochi, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item One of 9 students chosen worldwide as part of the JSoC program, sponsored by the Moore Foundation and MIT.
\item Created a Julia package,Compose3D.jl for 3D declarative graphics. 
\item Implemented custom web components for three.js using Google's Polymer library. 
\item Using the three.js custom web components, created ThreeJS.jl to create 3D graphics for the web directly from Julia.
\item Developed applications to render surf and mesh plots interactively based on ThreeJS.jl.
\item \href{https://github.com/rohitvarkey/ThreeJS.jl}{https://github.com/rohitvarkey/ThreeJS.jl}
\item \href{https://github.com/rohitvarkey/Compose3D.jl}{https://github.com/rohitvarkey/Compose3D.jl}
\end{tightemize}
\sectionsep

\runsubsection{RapidValue Solutions}
\descript{| Software Intern }
\location{May 2014 – June 2014 | Kochi, India}
\begin{tightemize}
\item Worked on iBeacon technology.
\item Created a Proof Of Concept application to demonstrate applications of iBeacon Technology in retail.
\item The PoC was further developed into a full fledged product.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\custombold{Programming:} Python \textbullet{} C \textbullet{} UNIX shell \textbullet{} C++ \textbullet{} JavaScript \textbullet{} Julia \textbullet{} \LaTeX\\
\custombold{Web Development:} Django \textbullet{} REST APIs \textbullet{} Nginx \textbullet PostgreSQL \textbullet  HTML \textbullet{} CSS \textbullet{} Polymer \textbullet Meteor \textbullet Node.js \textbullet Bower \textbullet Bootstrap3 
\section{Presentations}
\runsubsection{JuliaCon 2016}
\descript{| MIT, Cambridge, MA}
\location{ThreeJS.jl: Interactive 3D Graphics in the Browser using Julia}

\runsubsection{JuliaCon India 2015}
\descript{| Bangalore, India}
\location{ Interactive 3D Visualizations in Julia}

\runsubsection{JuliaCon 2015}
\descript{| MIT, Cambridge, MA (over video)}
\location{Compose3D.jl}
\end{minipage} 
\hfill
\begin{minipage}[t]{0.49\textwidth} 

\section{Projects}

\runsubsection{Smriti}
\descript{| A Portal for college memories}
\sectionsep
\begin{tightemize}
\item Wrote scripts to parse Google form data, create users with random passwords and send out emails to 900 students.
\item Developed a web portal for testimonials to be shared using Django.
\item Generated PDFs of profiles of each student to provide personalized hard copies for every student.
\end{tightemize}

\runsubsection{Healthizen}
\descript{| Synergy for a pristine Bengaluru}
\begin{tightemize}
\item Developed a web application to crowdsource health and sanitary issue reports in Bangalore in association with the Karnataka State Government.
\item Implemented the backend in Django with a REST API.
\item Ran database migrations on the production server successfully.
\item \href{http://healthizen.org/}{http://healthizen.org/}
\end{tightemize}

\runsubsection{Phosphene}
\descript{| A Python music processing library for hand made devices}
\begin{tightemize}
\item Added support for realtime music processing.
\item Implemented the reactive paradigm, providing users with a natural way to work with music signals.
\item Interfaced with several electronic devices to manipulate them according to the music using serial communication.
\item \href{https://github.com/rohitvarkey/phosphene}{https://github.com/rohitvarkey/phosphene}
\end{tightemize}

\runsubsection{TJNite}
\descript{| Colors on phones with the beat}
\begin{tightemize}
\item Developed an application to sync colors on the crowds phones in tune with the beat of the music being played.
\item Maintained websockets connections to push updates to mobile browsers.
\item \href{https://github.com/rohitvarkey/TJNite}{https://github.com/rohitvarkey/TJNite}
\end{tightemize}
\section{Publications}
\href{http://link.springer.com/article/10.1007/s13278-015-0274-0}{[1] Pranav Thulasiram Bhat , \custombold{Rohit Varkey Thankachan}, and K. Chandrasekaran. \textbf{"Sharding distributed social databases using social network analysis."} Social Network Analysis and Mining 5.1 (2015): 1-11.}
\section{Leadership}
\sectionsep
\begin{tightemize}
\item \custombold{President} and \custombold{Code Special Interest Group Head} | Institution of Engineers NITK Chapter, 2015-2016
\item \custombold{Joint Convenor} | Technites, Engineer NITK 2015
\end{tightemize}
\end{minipage} 
\end{document}  \documentclass[]{article}